Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2015-08-25 writeup/gz_hubble_data.tex
updates to writeup

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
\caption{a caption. Add scale in $p_{\rm features}$ somehow that doesn't clutter the plot even more. }
\label{fig:p_vs_p}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distribution of things for 3 groups. }
\label{fig:z_mu_p}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased vs weighted values for 3 groups.}
\label{fig:features_corrections}
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness vs. redshift of 118,083 galaxies in the ACS Hubble sample. The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure \ref{fig:p_vs_p}.}

\label{fig:features_corrections}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
\caption{Effects of redshift bias in 3,959 images in the \ferengi{} sample. Each point in a given redshift and surface brightness bin represents a unique galaxy. On the y-axis in each bin is the $p_{features}$ value of the image of that galaxy redshifted to the value corresponding to that redshift bin. On the x-axis is the $p_{features}$ value of the image of the same galaxy redshifted to $z=0.3$. Regions in which there is a nearly one-to-one relationship between $p_{features}$ at high redshift and $z=0.3$ are white; those in which there is not are green, and those with not enough data ($N<5$) are purple. }
\label{fig:p_vs_p}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full Hubble sample. The uncorrectable galaxies tend towards higher redshift, slightly lower in surface brightness, and lower values of $p_{features}$ than the correctable galaxies. The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
\label{fig:z_mu_p}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the Hubble sample.}

\label{fig:features_corrections}
\end{center}
\end{figure*}
